Regular singular Volterra equations on complex domains

### 2023-07-27 reg-sing-volterra.tex
Remove old version of main result
We'll remember this ponderous, unreadable statement fondly.

The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to $0$. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
\end{thm}
\begin{thm}
Suppose $\hardpart$ satisfies Condition~\eqref{cond:slow} from Section~\ref{setting:basic}. Then the solution $f_0$ from Theorem~\ref{thm:basic_volterra} is uniformly of exponential type $\lambda_0$ \textcolor{orange}{[explain what we mean by ``uniformly'']}. In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}
\begin{thm}\label{thm:perturbed_volterra}
\textcolor{DarkTurquoise}{Existence and uniqueness for perturbed operator}
Let $g$ be a function in the space $\in\singexp{\sigma+\epsilon}{A}(\Omega)$ defined in Section~\ref{fn-spaces}. The Volterra equation
\[ f = \Big[\hardpart +\softpart \Big] f + g \]
given by an operator of the kind described in Sections \ref{setting:basic} and \ref{setting:perturbed}, admits a unique solution $f$ that belongs to $\singexp{\sigma+\epsilon}{\Lambda}(\Omega)$, for every $\Lambda\geq A$ \textcolor{magenta}{[check]}. 
\end{thm}

\textcolor{DarkTurquoise}{The result below might not be stated perfectly, but it gives at least a rough sense of what I expect. It's an improved version of the result stated in Section~\ref{frac_int_exist}, which is copied from {\tt airy-resurgence}. Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}
\color{RoyalBlue}
\begin{thm}
Let $\Omega$ be an acute-angled open sector around $\zeta = 0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.} Over $\Omega$, consider a Volterra operator
\[ \mathcal{P} = p + \partial^{-1} \circ q + \mathcal{R}, \]
where
\begin{itemize}
\item $p$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item a simple zero at $\zeta = 0$,
\item no zeros in $\Omega$ (as the next condition implies), and
\item a positive lower bound $C_p |z|^d \le |p|$;
\end{itemize}
\item $q$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item an upper bound $|q| \le C_q |z|^{d-1}$; and
\end{itemize}
\item $\mathcal{R}$ is an integral kernel operator
\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta, \]
where $k$ is a holomorphic function on $\Omega^2$, with
\begin{itemize}
\item an exponential upper bound $k(a, a') \le C_k e^{A|\zeta(a) - \zeta(a')|}$,
\item \textcolor{orange}{[bound K soft]} \[ | k (a, a') |\le \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} e^{\Lambda|\zeta(a)-\zeta(a')|}\]
\end{itemize}
\end{itemize}
Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$, and let $\tau = q_0 / p_1$.

For any $\epsilon > 0$, when the constant $\Lambda > A$ is large enough, the regular singular Volterra equation
\[ \mathcal{P}f = 0 \]
has a unique solution in the affine subspace
\[ \zeta^{\tau-1} + \holoL{\infty, \tau-1+\epsilon}_\Lambda(\Omega) \]
of the function space $\holoL{\infty, \tau-1}_\Lambda(\Omega)$, defined in Section~\ref{fn-spaces}.
\end{thm}
\color{black}
%%\begin{thm}
%%Let $\Omega$ be an acute-angled sector around $0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}

>>>>

The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to $0$. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
\end{thm}
\begin{thm}
Suppose $\hardpart$ satisfies Condition~\eqref{cond:slow} from Section~\ref{setting:basic}. Then the solution $f_0$ from Theorem~\ref{thm:basic_volterra} is uniformly of exponential type $\lambda_0$ \textcolor{orange}{[explain what we mean by ``uniformly'']}. In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}
\begin{thm}\label{thm:perturbed_volterra}
\textcolor{DarkTurquoise}{Existence and uniqueness for perturbed operator}
Let $g$ be a function in the space $\in\singexp{\sigma+\epsilon}{A}(\Omega)$ defined in Section~\ref{fn-spaces}. The Volterra equation
\[ f = \Big[\hardpart +\softpart \Big] f + g \]
given by an operator of the kind described in Sections \ref{setting:basic} and \ref{setting:perturbed}, admits a unique solution $f$ that belongs to $\singexp{\sigma+\epsilon}{\Lambda}(\Omega)$, for every $\Lambda\geq A$ \textcolor{magenta}{[check]}. 
\end{thm}
%%\begin{thm}
%%Let $\Omega$ be an acute-angled sector around $0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}
